---
title: "ch20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(purrr)
```

# Vectors

##20.3.5
1. the difference between is.finite(x) and !is.finite(x) is that the ! means not therefore the second one is saying is not and will exclude those things.
2. this allows numerical tollerance when working with floating point numbers
```{r}
dplyr::near
```
3.An integer vector can take 232 values. A double vector can take 3 values. 
4. one possible way of converting a double to an integer is by putting a L after the number. Another way is with the type.convert code. A third way is with the as.integer code. 
5. parse_logical, parse_integer, parse_double

## 20.4.6
1. mean(is.na(x)) tells you what proportion is "not available". sum(!is.finite(x)) tells you how many are not finite
2. is.vector gives a true if x is a vector of the specified mode having no attributes other than names. It will be true for list and expression as well.
3. both will set name to an object but setNames has more features and is stricter
4. 1.[[]] because it is asking for a specific value 2. even_num  3.except_last
5. which will ignore NAs
6. both will give an NA

## 20.5.4
2. a tibble subset will return a tibble and a list subset will return a vector
## 20.7.4
1.it prints in hours
```{r}
hms::hms(3600)
```
2.the length must be the same or else you will get an error
3. yes as long as the columns are the same length.